Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-02-11 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
Applying referee's simple corrections

\usepackage[]{latexsym}
\usepackage{graphicx}

@@

\title{Reinforcement learning for options\\on target volatility funds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}}

@@

\institute{Financial Engineering, Intesa Sanpaolo Group,\\
Largo Mattioli 3, 20121 Milan, Italy\\
\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
Financial Engineering, Marketz S.p.A.,\\
Corso Europa, 2, 20122 Milan, Italy\\
\email{Emanuele.Nastasi@marketz.eu} \and Financial Engineering,
X-Numeris S.r.l.,\\ Via Turro, 7 , 20127 Milan, Italy\\
\email{Stefano.Polo@xnumeris.com}}

@@

\begin{abstract}
We deal with the funding costs rising from hedging the risky securities underlying a target volatility strategy (TVS), a portfolio of risky assets and a risk-free one dynamically rebalanced in order to keep the realized volatility of the portfolio on a certain level. The uncertainty in the TVS risky portfolio composition along with the difference in hedging costs for each component requires to solve a control problem to evaluate the option prices. We derive an analytical solution of the problem in the Black and Scholes (BS) scenario. Then we use Reinforcement Learning (RL) techniques to determine the fund composition leading to the most conservative price under the local volatility (LV) model, for which an {\it a priori} solution is not available. We show how the performances of the RL agents are compatible with those obtained by applying path-wise the BS analytical strategy to the TVS dynamics, which therefore appears competitive also in the LV scenario.

@@

\section{Introduction}
In the recent years portfolio managers are exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such an environment is given by target volatility strategies (TVSs) (also known as constant volatility targeting) which are able to preserve the portfolio at a predetermined level of volatility. A TVS is a portfolio of risky assets (typically  equities) and a risk-free asset dynamically re-balanced with the aim of maintaining the overall portfolio volatility level closed to some target value. The constant volatility approach can help investors to obtain desired risk exposures over the short and long term and it increases the risk-adjusted performance of the portfolio.

These products were initially offered in the Asian markets, see for instance the reports of \cite{Chew2011} and \cite{Xue2012}, which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \cite{Morrison2013}. At the present day we can observe some new market indices based on the mechanism of the target volatility strategy such as Dow Jones Volatility Control Index, and S\&P 500 Risk Control Index.

In the recent literature TVSs are tested to investigate their performances in term of realized returns, see for instance \cite{Hocquard2013} and \cite{Perchet2016}, and the soundness of the volatility targeting algorithm, as described in \cite{Kim2018}. Moreover, in the present day, in the derivative market new structured financial products that see TVSs as underlying are becoming widely used by practitioners. Those derivative instruments are known as target volatility options (TVOs) and have gained great interest in the derivative pricing literature, see in particular \cite{Albeverio2019}, \cite{DiGraziano2012}, \cite{DiPersio2019}, and \cite{Grasselli2016}.

@@

Although from a theoretical point of view this solution represents a sub-optimal strategy when dealing with generic dynamics for the risky assets, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem. More precisely we numerically study the problem in the general case of a local volatility dynamics \cite{Derman1994}, \cite{Dupire1994}  by adopting a Reinforcement Learning approach, in particular an \textit{ad hoc} vanilla direct policy algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. 
\\

The paper is organized as follows. In Section \ref{sec:TVS} we introduce more in detail the manager-bank contract and provide the description of the TVS dynamics in presence of valuation adjustments such as the hedging costs. Then, in Section \ref{sec:Derivative} we introduce the structured class of derivative contracts linked to TVSs, where we describe the arising dynamical control problem for pricing those options. Moreover in this section we derive the BS closed solution for European TVOs in two different ways: one applying the Gy\"ongy Lemma and the other by writing the Hamilton-Jacobi-Bellman equation. In Section \ref{sec:RL} we illustrate how we have applied RL to solve the dynamic control problem, giving a description of the algorithm we have built. We conclude the paper with Section \ref{sec:Numerical_investigations} where we present the numerical results obtained in this work for the Black and Scholes model and the local volatility one.
\\

@@

\section{Target volatility strategy}\label{sec:TVS}
As mentioned before, this work aims to enrich the TVS pricing literature by studying the aspect related to the funding costs coming from hedging the risky assets underlying a target volatility portfolio. Thus we consider the following scenario: a bank selling a protection to a portfolio manager who has his capital invested in a TVS. In our case the fund manager has the freedom of changing the relative weights of the risky asset during the life of the TVS; once the allocation strategy is selected then the volatility targeting algorithm rebalances the risky component of the portfolio with the risk-free one in order to keep the overall portfolio volatility close to a target value. Clients investing in the fund pay a running fee for the service of the fund manager and their capital is protected.

The fund manager usually buys from a bank an option on the TVS to ensure capital protection. For instance, the capital can be protected by buying a put option. In this case, we can write the net asset value (NAV) $A_t$ of the strategy as given by\footnote{Here we neglect discounting factors.}
\begin{equation}
    A_t \coloneqq \max\{V_t,K\} = V_t + (K-V_t)^+ \; ,
\end{equation}
where $V_t$ is the price process of the strategy, and $K$ is the guaranteed capital. On the other hand, the fund manager can replicate the payoff by means of the put-call parity by investing the capital in a low-risk asset and buying a call on the strategy
\begin{equation}
    A_t = K + (V_t-K)^+ \; .
\end{equation}

In this way, the TVS is only defined in the two contracts client-fund and fund-bank. The fund manager is not implementing the strategy by trading in the market, and he is not subject to additional costs to access the market. On the other way, the bank is paying such costs since she is actively hedging the call option sold to the manager.  The bank trading activity implemented to actively hedge the option requires funding the collateral procedures of the hedging instruments along with any lending/borrowing fee.
We remark that the choices of the manager trading activity are stochastic processes since they will depend on the market evolution. Thus, neither the manager strategy nor the bank financing costs for hedging the option can be written in the fund-bank contract. For this reason, the price of a financial product sold by the bank is adjusted to include any valuation adjustment due to the trading activity.

@@

\subsection{The strategy Price Process}
We work on a filtered probability space $\left(\Omega, \mathcal{F}, \{\mathcal{F}_t\}_{t\geq0}, \mathbb{P}  \right)$ satisfying the usual assumptions for a market model, where $\mathbb{P}$ is the physical probability measure representing the actual distribution of supply and demand shocks on equities prices.

We consider a fund trading a basket of $n$ risky securities with price process $S_t = (S_t^i, \, i=1,\dots,n)$ funded with a cash account $B_t$ accruing at $r_t$. Any dividend paid by the securities is re-invested in the fund. Here, we assume that the TVS is implemented in continuous time, even if in the practice we can implement the strategy only on a discrete set of dates. We introduce the deflated gain process $\Bar{G}_t^i$ associated with the risky securities as given by
\begin{equation}
    \Bar{G}_t^i \coloneqq \Bar{S}_t^i + \Bar{D}_t^i \; ,
\end{equation}
where we define the deflated price and cumulative dividend processes as 
\begin{equation}
    \bar{S}_t^i \coloneqq \frac{S_t^i}{B_t} \; , \quad \bar{D}^i_t \coloneqq \int_0^t\frac{d\pi_u^i}{B_u} + \int_0^t\frac{d\psi_u^i}{B_u} \; ,
\end{equation}
where $\pi^i_t$ represents the cumulative contractual-coupon process paid by the security, and $\psi_t^i$ represents the cumulative valuation adjustments.
Since fund managers allocating TVS usually rely on equity assets, here we use the results of \cite{Gabrielli2020} that analyzes the valuation adjustments for equity products. We can write 
\begin{equation}
    \psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du \; ,
\label{eq:XVA_equity}\end{equation}
where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

@@

Now, in order to prevent arbitrages, we assume the existence of a risk-neutral measure $\mathbb{Q}$ equivalent to $\mathbb{P}$ under which the deflated gain processes of all traded securities are martingales. Under this assumption, we are able to derive the drift conditions on the security price processes, and in turn on the strategy price process.
\begin{equation}
    \forall u >t \quad \bar{G}_t^i = \mathbb{E}_t \left[\bar{G}_u^i\right] \quad\Longrightarrow \quad dS_t^i = r_tS_t^idt-d\pi_t^i-d\psi_t^i + dM_t^i \; ,
\label{eq:risk_neutral}\end{equation}
where $M_t^i$ are martingale under $\mathbb{Q}$. If we substitute this expression for the security dynamics into the definition of the strategy we can check that the price process of the strategy is accruing at a cash account rate $r_t$ compensated for the fund manager fees
\begin{equation}
    dV_t = V_t(r_t-\phi_t)dt + dM_t^V \; ,
\end{equation}
with $M_t^V$ martingale under $\mathbb{Q}$. Notice that, as expected from non-arbitrage considerations, the coupons paid by each security appear only in the drift of the security price process, but they do not impact the drift of the strategy.

@@

\subsection{The Volatility Targeting Constraint}
In a typical TVS, the fund manager selects a risky-asset portfolio with a specific time-dependent allocation strategy expressed by means of the vector of relative weights $\alpha_t$, along with a risk-free asset, which we can identify with the bank account $B_t$. In the following, for sake of simplicity in exposition, we consider only total-return securities, namely we set $\pi_t=0$. Thus we can write Equation~\eqref{eq:TVS_first} as given by
\begin{equation}
    \frac{dI_t}{I_t}= \omega_t \alpha_t \cdot \frac{dS_t}{S_t} + \left(1-\omega_t  \alpha_t \cdot \mathds{1} \right)\frac{dB_t}{B_t}- \phi_t dt \; ,
\label{eq:TVS_elegant}\end{equation}
where $\mathds{1}$ is a $n$-dimensional vector of ones and $\omega_t\in[0,1]$ is determined so that the strategy log-normal volatility is kept constant, namely
\begin{equation}
        \omega_t: \quad \mathrm{Var}_t[dI_t] = \bar{\sigma}^2I_t^2dt \; ,
\end{equation}
where $\Bar{\sigma}$ is the target volatility value.
In practice, this means that the fund manager will select a risky-portfolio choosing $\alpha_t$ equities from the universe where he can trade and after that, his choices will be scaled by the automatic target volatility algorithm $\omega_t$.\footnote{We recall that the universe of assets where the manager can trade and the value of $\bar{\sigma}$ are written in the contract.}

To derive the expression for $\omega_t$ we need to assume a generic continuous semi-martingales dynamics under the risk-neutral measure for the underlying securities, so that we can write Equation~\eqref{eq:risk_neutral} as 
\begin{equation}
    \frac{dS_t^i}{S_t^i} = \left(r_t - \mu_t^i \right)dt + \nu_t^i \cdot dW_t \; ,
\label{eq:Equity_process}\end{equation}
where $\nu_t$ is an adapted matrix process ensuring the existence of a solution for the stochastic differential equation (SDE) and $W_t$ is a $n$-dimensional vector of Brownian motions under $\mathbb{Q}$. Under these assumptions we can derive an expression for $\omega_t$, and we get\footnote{In all formulae the norm for a vector $a$ is defined as $\|a\|\coloneqq\sqrt{a\cdot a}$.}
\begin{equation}
    \omega_t = \frac{\Bar{\sigma}}{\norm{ \alpha_t\cdot \nu_t }} \; .
\end{equation}
Hence, putting this last result in the dynamics of $I_t$ we obtain

@@

\subsection{European Options}
If the derivative contract depends only on the marginal distribution of $I_T$ at maturity (a European payoff), we are able to calculate an optimal strategy. We consider the following pricing problem
\begin{equation}
    V_0 \coloneqq \sup_\alpha \mathbb{E}_0\left[D(0,T;\zeta)\Phi(I_T(\alpha))\right] \; ,
\end{equation}
where $\Phi$ is the payoff function of the derivative.

@@

\subsection{Black and Scholes model}\label{subsec:BS_model}
In the time-dependent Black and Scholes model with deterministic rates, we can work with empty $X_t$, since in this case the portfolio dynamics \eqref{eq:TVS_last} is Markovian, leading to an optimal strategy $\alpha_t^*$ which depends in principle only on $I_t$. As a consequence, the local drift defined in Equation~\eqref{eq:local_drift} can be written as
\begin{equation}
     \ell_\alpha \left(t,K\right) = \bar{\sigma}   \frac{\mu\left(t\right) \cdot \alpha\left(t,K\right)}{\norm{\alpha\left(t,K\right) \cdot \nu\left(t\right)}} \; ,  
\end{equation}
so that the optimization problem can be solved by looking only at the Markovian projection without simulating all the Brownian motions $W_t$. Notice that we are indicating the dependency on time in parenthesis to highlight that in this formula all the quantities are deterministic functions of time.

@@

\begin{proposition}
When the underlying securities follow a Black and Scholes model with deterministic rates, the optimal strategy for a non-decreasing European payoff consists in minimizing the local drift function, independently of the current state $I_t$
\begin{equation}
    \alpha^*(t) \coloneqq \argmin_\alpha \frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t) \|} \; .
\label{eq:BS_optimal_strategy}
\end{equation}
Analogously, the optimal strategy for a non-increasing European payoff consists in maximizing the local drift function:
\begin{equation}
    \alpha^*(t) \coloneqq \argmax_\alpha \frac{\alpha \cdot \mu(t)}{\norm{\alpha \cdot \nu(t)}} \; .
\label{eq:BS_optimal_strategy_put}
\end{equation}
\end{proposition}
The absence of stochastic elements in Equation~\eqref{eq:BS_optimal_strategy} makes the optimal strategy known \textit{a priori} with no simulation needed; in fact one can solve the optimization problem once for all $\forall t \in \mathcal{T}$ just looking at the market data $\mu(t)$ and $\nu(t)$ for the securities. Once $\alpha^*$ is known, then one can price the payoff by the following BS formula
\begin{equation}
	V_0^{\text{BS}} = BS(F^{\text{TVS}}(0,T;\alpha^*), K, T, \bar{\sigma}, D(0,T;\zeta)) \; ,
\label{eq:bs_closed_solution}\end{equation}
where $F^{\text{TVS}}(t,T;\alpha)$ is the TVS forward curve defined by
\begin{equation}
	F^{\text{TVS}}(t,T;\alpha) = I_t \exp\left[\int_t^T\left(r(u)-\ell_{\alpha} \left(u\right)\right)du\right] \; ,
\label{eq:tvs_forward}\end{equation}
while $BS(F,K,T,\sigma,D)$ is the standard BS formula for a European option with forward curve $F$, strike $K$, time to maturity $T$, volatility $\sigma$ and discount factor $D$.

In Figure~\ref{fig:strategy_price_comparison} we provide a comparison among the option price obtained with the optimal strategy (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and those with other intuitive strategies (S$_A$, S$_B$, S$_C$). Here we consider the case of an at-the-money call option with spot $I_0 = 1\, \text{EUR}$, maturity $T=5 \, \text{yr}$, target volatility $\bar{\sigma}=5\%$, and a nonnegative constraint on $\alpha$. The intuitive strategies are
\begin{itemize}
\item S$_A$: invest all in the asset with the maximum forward curve at maturity;
\item S$_B$: for each market pillar before maturity invest all in the asset with minimum $\mu(t)$; 
\item S$_C$: for each market pillar before maturity invest all in the asset with minimum $\mu(t)/\|\nu(t)\|$.
\end{itemize}
As the reader can observe, our strategy outperforms any other intuitive one a practitioner might adopt.
\begin{figure}[t]
	\centering
	\includegraphics[width=4in]{strategy_price_comparison_grey.eps}
	\caption{Comparison of plain vanilla prices on the TVS by adopting different allocation strategies: the optimal Black and Scholes solution (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and other intuitive strategies (S$_A$, S$_B$, S$_C$)}
	\label{fig:strategy_price_comparison}
\end{figure}

>>>>

\usepackage[]{latexsym}
\usepackage{graphicx}
\usepackage{xcolor}

@@

\title{Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}}

@@

\institute{Financial Engineering, Intesa Sanpaolo Group,\\
Largo Mattioli 3, 20121 Milan, Italy\\
\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
Financial Engineering, Marketz S.p.A.,\\
Corso Europa, 2, 20122 Milan, Italy\\
\email{Emanuele.Nastasi@marketz.eu} \and \change{Financial Risk Methodologies, Unicredit S.p.A.,\\ Piazza Gae Aulenti, 3, 20154 Milan, Italy \\ \email{Stefano.Polo@unicredit.eu}}
\remove{Financial Engineering,
X-Numeris S.r.l.,\\ Via Turro, 7 , 20127 Milan, Italy\\
\email{Stefano.Polo@xnumeris.com}}}

@@

\begin{abstract}
We deal with the funding costs rising from hedging the risky securities underlying a target volatility strategy (TVS), a portfolio of risky assets and a risk-free one dynamically rebalanced in order to keep the realized volatility of the portfolio on a certain level. The uncertainty in the TVS risky portfolio composition along with the difference in hedging costs \change{of its} \remove{for each} component requires to solve a control problem to evaluate the option prices. We derive an analytical solution of the problem in the Black and Scholes (BS) scenario. Then we use Reinforcement Learning (RL) techniques to determine the fund composition leading to the most conservative price under the local volatility (LV) model, for which an {\it a priori} solution is not available. We show how the performances of the RL agents are compatible with those obtained by applying path-wise the BS analytical strategy to the TVS dynamics, which therefore appears competitive also in the LV scenario.

@@

\section{Introduction}
In the recent years portfolio managers are exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such an environment is given by target volatility strategies (TVSs)\change{,} \remove{(}also known as constant volatility targeting\remove{)}\change{,} which are able to preserve the portfolio at a predetermined level of volatility. A TVS is \change{a strategy for managing} a portfolio of risky assets (typically  equities) and a risk-free \change{one} \remove{asset} dynamically re-balanced with the aim of maintaining the overall portfolio volatility level closed to some target value. The constant volatility approach can help investors to obtain desired risk exposures over the short and long term and \change{possibly} it increases the risk-adjusted performance of the portfolio.

These products were initially offered in the Asian markets, see for instance \remove{the reports of} \cite{Chew2011} and \cite{Xue2012}, which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \cite{Morrison2013}. At the present day we can observe some new market indices based on the mechanism of the target volatility strategy such as Dow Jones Volatility Control Index, and S\&P 500 Risk Control Index.

In the recent literature\change{,} \remove{TVSs} \change{TVS-based portfolios} are tested to investigate their performances in term of realized returns, see for instance \cite{Hocquard2013} and \cite{Perchet2016}, and the soundness of the volatility targeting algorithm, as described in \cite{Kim2018}. Moreover, in the present day, in the derivative market new structured financial products that see TVSs as underlying are becoming widely used by practitioners. Those derivative instruments are known as target volatility options (TVOs) and have gained great interest in the derivative pricing literature, see in particular \cite{Albeverio2019}, \cite{DiGraziano2012}, \cite{DiPersio2019}, and \cite{Grasselli2016}.

@@

Although from a theoretical point of view this solution represents a sub-optimal strategy when dealing with generic dynamics for the risky assets, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem. More precisely we numerically study the problem in the general case of a local volatility dynamics \cite{Derman1994}, \cite{Dupire1994}  by adopting a Reinforcement Learning approach, in particular an \textit{ad hoc} \remove{vanilla} direct policy \change{search} algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. 
\\

The paper is organized as follows. In Section \ref{sec:TVS} we introduce more in detail the manager-bank contract and provide the description of the TVS dynamics in presence of valuation adjustments such as the hedging costs. Then, in Section \ref{sec:Derivative} we introduce the structured class of derivative contracts linked to TVSs, where we describe the arising dynamical control problem for pricing those options. Moreover in this section we derive the BS closed solution for European TVOs in two different ways: one applying the Gy\"ongy Lemma and the other \change{through} \remove{by writing} the Hamilton-Jacobi-Bellman equation. In Section \ref{sec:RL} we illustrate how we have applied RL to solve the dynamic control problem, giving a description of the algorithm we have built. We conclude the paper with Section \ref{sec:Numerical_investigations} where we present the numerical results obtained in this work for the Black and Scholes model and the local volatility one.
\\

@@

\section{Target \change{V}olatility \change{S}trategy}\label{sec:TVS}
As mentioned before, this work aims to enrich the TVS pricing literature by studying the aspect related to the funding costs coming from hedging the risky assets underlying a target volatility portfolio. Thus we consider the following scenario: a bank selling a protection to a portfolio manager who has his capital invested \change{according to} \remove{in} a TVS. In our case the fund manager has the freedom of changing the relative weights of the risky asset during the life of the TVS; once the allocation strategy is selected then the volatility targeting algorithm rebalances the risky component of the portfolio with the risk-free one in order to keep the overall portfolio volatility close to a target value. Clients investing in the fund pay a running fee for the service of the fund manager and their capital is protected.

The fund manager usually buys from a bank an option on the TVS to ensure capital protection. For instance, the capital can be protected by buying a put option. In this case, we can write the \change{undiscounted} net asset value (NAV) $A_t$ of the strategy as given by\footnote{\remove{Here we neglect discounting factors.}}
\begin{equation}
    A_t \coloneqq \max\{V_t,K\} = V_t + (K-V_t)^+ \; ,
\end{equation}
where $V_t$ is the price process of the strategy, and $K$ is the guaranteed capital. On the other hand, the fund manager can replicate the payoff by means of the put-call parity by investing the capital in a low-risk asset and buying a call on the strategy
\begin{equation}
    A_t = K + (V_t-K)^+ \; .
\end{equation}

In this way, the TVS is only defined in the two contracts client-fund and fund-bank. The fund manager is not implementing the strategy by trading in the market, and he is not subject to additional costs to access the market. On the other way, the bank is paying such costs since \change{it} \remove{she} is actively hedging the call option sold to the manager.  The bank trading activity implemented to actively hedge the option requires funding the collateral procedures of the hedging instruments along with any lending/borrowing fee.
We remark that the choices of the manager trading activity are stochastic processes since they will depend on the market evolution. Thus, neither the manager strategy nor the bank financing costs for hedging the option can be written in the fund-bank contract. For this reason, the price of a financial product sold by the bank is adjusted to include any valuation adjustment due to the trading activity.

@@

\subsection{The \change{S}trategy Price Process}
We work on a filtered probability space $\left(\Omega, \mathcal{F}, \{\mathcal{F}_t\}_{t\geq0}, \mathbb{P}  \right)$ satisfying the usual assumptions for a market model, where $\mathbb{P}$ is the physical probability measure \remove{representing the actual distribution of supply and demand shocks on equities prices}.

We consider a fund trading a basket of $n$ risky securities with price process \change{$S_t = \{S_t^i, \, i=1,\dots,n\}$} \remove{$S_t = (S_t^i, \, i=1,\dots,n)$} funded with a cash account $B_t$ accruing at $r_t$. Any dividend paid by the securities is re-invested in the fund. Here, we assume that the TVS is implemented in continuous time, even if in the practice we can implement the strategy only on a discrete set of dates. We introduce the deflated gain process $\Bar{G}_t^i$ associated with the risky securities as given by
\begin{equation}
    \Bar{G}_t^i \coloneqq \Bar{S}_t^i + \Bar{D}_t^i \; ,
\end{equation}
where we define the deflated price and cumulative dividend processes as 
\begin{equation}
    \bar{S}_t^i \coloneqq \frac{S_t^i}{B_t} \; , \quad \bar{D}^i_t \coloneqq \int_0^t\frac{d\pi_u^i}{B_u} + \int_0^t\frac{d\psi_u^i}{B_u} \; ,
\end{equation}
where $\pi^i_t$ represents the cumulative contractual-coupon process paid by the security, and $\psi_t^i$ represents the cumulative valuation adjustments.
Since fund managers allocating TVS usually rely on equity assets, here we use the results of \cite{Gabrielli2020} that analyzes the valuation adjustments for equity products. We can write 
\begin{equation}
    \psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du \; ,
\label{eq:XVA_equity}\end{equation}
where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

@@

Now, in order to prevent arbitrages, we assume the existence of a risk-neutral measure $\mathbb{Q}$ equivalent to $\mathbb{P}$ under which the deflated gain processes of all traded securities are martingales. Under this assumption, we are able to derive the drift conditions on the security price processes, and in turn on the strategy price process\change{, that is}
\begin{equation}
    \forall u >t \quad \bar{G}_t^i = \mathbb{E}_t \left[\bar{G}_u^i\right] \quad\Longrightarrow \quad dS_t^i = r_tS_t^idt-d\pi_t^i-d\psi_t^i + dM_t^i \; ,
\label{eq:risk_neutral}\end{equation}
where $M_t^i$ are martingale under $\mathbb{Q}$. If we substitute this expression for the security dynamics into the definition of the strategy we can check that the price process of the strategy is accruing at \change{the following} \remove{a} cash account rate $r_t$ compensated for the fund manager fees
\begin{equation}
    dV_t = V_t(r_t-\phi_t)dt + dM_t^V \; ,
\end{equation}
with $M_t^V$ martingale under $\mathbb{Q}$. Notice that, as expected from non-arbitrage considerations, the coupons paid by each security appear only in the drift of the security price process, but they do not impact the drift of the strategy.

@@

\subsection{The Volatility Targeting Constraint}
In a typical TVS, the fund manager selects a risky-asset portfolio with a specific time-dependent allocation strategy expressed by means of the vector of relative weights $\alpha_t$, along with a risk-free asset, which we can identify with the bank account $B_t$. In the following, for sake of simplicity in exposition, we consider only total-return securities, namely we set $\pi_t=0$ \change{since no dividends are paid}. Thus we can write Equation~\eqref{eq:TVS_first} as given by
\begin{equation}
    \frac{dI_t}{I_t}= \omega_t \alpha_t \cdot \frac{dS_t}{S_t} + \left(1-\omega_t  \alpha_t \cdot \mathds{1} \right)\frac{dB_t}{B_t}- \phi_t dt \; ,
\label{eq:TVS_elegant}\end{equation}
where $\mathds{1}$ is a $n$-dimensional vector of ones and $\omega_t\in[0,1]$ is determined so that the strategy log-normal volatility is kept constant, namely
\begin{equation}
        \omega_t: \quad \mathrm{Var}_t[dI_t] = \bar{\sigma}^2I_t^2dt \; ,
\end{equation}
where $\Bar{\sigma}$ is the target volatility value.
In practice, this means that the fund manager will select a risky-portfolio choosing $\alpha_t$ equities from the universe where \change{s}he can trade and after that, \change{her} \remove{his} choices will be scaled by the automatic target volatility algorithm $\omega_t$.\footnote{We recall that the universe of assets where the manager can trade and the value of $\bar{\sigma}$ are written in the contract.}

\remove{To derive the expression for $\omega_t$ we need to assume} \change{It is possible to derive the expression for $\omega_t$ assuming} a generic continuous semi-martingales dynamics under the risk-neutral measure for the underlying securities, so that \remove{we can write} Equation~\eqref{eq:risk_neutral} \change{can be written} as 
\begin{equation}
    \frac{dS_t^i}{S_t^i} = \left(r_t - \mu_t^i \right)dt + \nu_t^i \cdot dW_t \; ,
\label{eq:Equity_process}\end{equation}
where $\nu_t$ is an adapted matrix process ensuring the existence of a solution for the stochastic differential equation \remove{(SDE)} and $W_t$ is a $n$-dimensional vector of Brownian motions under $\mathbb{Q}$. Under these assumptions we can derive an expression for $\omega_t$, and we get\footnote{In all formulae the norm for a vector $a$ is defined as $\|a\|\coloneqq\sqrt{a\cdot a}$.}
\begin{equation}
    \omega_t = \frac{\Bar{\sigma}}{\norm{ \alpha_t\cdot \nu_t }} \; .
\end{equation}
Hence, putting this last result in the dynamics of $I_t$ we obtain

@@

\subsection{European Options}
If the derivative contract depends only on the marginal distribution of $I_T$ at maturity (\change{i.e.,} a European payoff), we are able to calculate an optimal strategy. We consider the following pricing problem
\begin{equation}
    V_0 \coloneqq \sup_\alpha \mathbb{E}_0\left[D(0,T;\zeta)\Phi(I_T(\alpha))\right] \; ,
\end{equation}
where $\Phi$ is the payoff function of the derivative.

@@

\subsection{Black and Scholes \change{Scenario}}\label{subsec:BS_model}
In the time-dependent Black and Scholes model with deterministic rates, we can work with empty $X_t$, since in this case the portfolio dynamics \eqref{eq:TVS_last} is Markovian, leading to an optimal strategy $\alpha_t^*$ which depends in principle only on $I_t$. As a consequence, the local drift defined in Equation~\eqref{eq:local_drift} can be written as
\begin{equation}
     \ell_\alpha \left(t,K\right) = \bar{\sigma}   \frac{\mu\left(t\right) \cdot \alpha\left(t,K\right)}{\norm{\alpha\left(t,K\right) \cdot \nu\left(t\right)}} \; ,  
\end{equation}
so that the optimization problem can be solved by looking only at the Markovian projection without simulating all the Brownian motions $W_t$. Notice that we are indicating the dependency on time in parenthesis to highlight that in this formula all the quantities are deterministic functions of time.

@@

\begin{proposition}
When the underlying securities follow a Black and Scholes \change{QUA IO LASCEREI MODEL (REFEREE PROPONE SCENARIO)} model with deterministic rates, the optimal strategy for a non-decreasing European payoff consists in minimizing the local drift function, independently of the current state $I_t$
\begin{equation}
    \alpha^*(t) \coloneqq \argmin_\alpha \frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t) \|} \; .
\label{eq:BS_optimal_strategy}
\end{equation}
Analogously, the optimal strategy for a non-increasing European payoff consists in maximizing the local drift function:
\begin{equation}
    \alpha^*(t) \coloneqq \argmax_\alpha \frac{\alpha \cdot \mu(t)}{\norm{\alpha \cdot \nu(t)}} \; .
\label{eq:BS_optimal_strategy_put}
\end{equation}
\end{proposition}
The absence of stochastic elements in Equation~\eqref{eq:BS_optimal_strategy} makes the optimal strategy known \textit{a priori} with no simulation needed; in fact one can solve the optimization problem once for all $\forall t \in \mathcal{T}$ just looking at the market data $\mu(t)$ and $\nu(t)$ for the securities. Once $\alpha^*$ is known, then one can price the payoff by the following BS formula
\begin{equation}
	V_0^{\text{BS}} = BS(F^{\text{TVS}}(0,T;\alpha^*), K, T, \bar{\sigma}, D(0,T;\zeta)) \; ,
\label{eq:bs_closed_solution}\end{equation}
where $F^{\text{TVS}}(t,T;\alpha)$ is the TVS forward curve defined by
\begin{equation}
	F^{\text{TVS}}(t,T;\alpha) = I_t \exp\left[\int_t^T\left(r(u)-\ell_{\alpha} \left(u\right)\right)du\right] \; ,
\label{eq:tvs_forward}\end{equation}
while $BS(F,K,T,\sigma,D)$ is the standard BS formula for a European option with forward curve $F$, strike $K$, time to maturity $T$, volatility $\sigma$ and discount factor $D$.

In Figure~\ref{fig:strategy_price_comparison} we provide a comparison among the option price obtained with the optimal strategy (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and those with \change{the below} \remove{other} intuitive strategies (S$_A$, S$_B$, S$_C$). Here we consider the case of an at-the-money call option with spot $I_0 = 1\, \text{EUR}$, maturity $T=5 \, \text{yr}$, target volatility $\bar{\sigma}=5\%$, and a nonnegative constraint on $\alpha$. The intuitive strategies are
\begin{itemize}
\item S$_A$: invest all in the asset with the maximum forward curve at maturity;
\item S$_B$: for each market pillar before maturity invest all in the asset with minimum $\mu(t)$; 
\item S$_C$: for each market pillar before maturity invest all in the asset with minimum $\mu(t)/\|\nu(t)\|$.
\end{itemize}
As the reader can observe, our strategy outperforms any other intuitive one a practitioner might adopt.
\begin{figure}[t]
	\centering
	\includegraphics[width=4in]{strategy_price_comparison_grey.eps}
	\caption{Comparison of plain vanilla prices on the TVS by adopting different allocation strategies: the optimal Black and Scholes solution (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and other intuitive strategies (S$_A$, S$_B$, S$_C$)}
	\label{fig:strategy_price_comparison}
\end{figure}

\subsubsection{Unconstrained Allocation Strategy: Closed Form Solution}
In absence of constraints on the allocation strategy, we are able to derive a closed form solution to the BS problem \eqref{eq:BS_optimal_strategy}.
\begin{lemma}
	Let \remove{be} $\mu, \alpha \in \mathbb{R}^n$, $\nu \in \mathbb{R}^{n\times n}$ be a full rank matrix and $\Sigma\coloneqq \nu \tr{\nu}$. Then the closed solution of the optimization problem \eqref{eq:BS_optimal_strategy} is 
	\begin{equation}
			\alpha^* = - \frac{\Sigma^{-1} \cdot \mu}{\norm{(\Sigma^{-1} \cdot \mu)\cdot \nu}} \; .
	\end{equation}
\end{lemma}
\begin{proof}
Since the argument of the minimum \eqref{eq:BS_optimal_strategy} is zero-homogeneous, then we can rewrite the problem as
\begin{equation}
		\begin{aligned}
			&\text { minimize } \alpha \cdot \mu\\
			&\text { subject to } \|\alpha \cdot \nu\|^2=1 \; .
	\end{aligned}
\end{equation}
By setting the Lagrangian function associated with the problem
\begin{equation}
	\mathcal{L}\left(\alpha, \lambda\right)=\alpha \cdot \mu-\lambda\left(\|\alpha \cdot \nu\|^2-1\right) \; ,
\end{equation}
we obtain the first order conditions
\begin{eqsys}
	\frac{\partial \mathcal{L}}{\partial \alpha}=\mu -2\lambda \Sigma \cdot \alpha=0 \\
	\frac{\partial \mathcal{L}}{\partial \lambda}= \norm{\alpha \cdot \nu}^2-1=0
	\; ,
\end{eqsys}
Then, by applying simple algebra, we obtain the analytical form for the free optimal strategy
\begin{equation}
	\alpha^* = \pm \frac{\Sigma^{-1} \cdot \mu}{\norm{(\Sigma^{-1} \cdot \mu)\cdot \nu}} \; .
\label{eq:analytical_solution_free_strategy}\end{equation}
We take the minus sign to get the minimum value of the TVS local drift while the plus sign for the maximum one (put payoff). $\Box$
\end{proof}
